\documentclass[12pt]{unlsilabsop}
\title{Backup and recovery}
\date{September 14, 2014}
\author{Frank Meier Aeschbacher}
\approved{Frank Meier Aeschbacher}
\sopid{002}
\sopversion{v0}
\sopabstract{Describes how parts used and produced during manufacturing are stored.}
\begin{document}

\maketitle

%------------------------------------------------------------------
\section{Scope}
This covers all computer systems involved in manufacturing modules.

%------------------------------------------------------------------
\section{Purpose}
Computer systems are used to control manufacturing processes, perform tests, and to store critical results. This document describes how the systems get backuped.

%------------------------------------------------------------------
%>\section{Definitions}

%------------------------------------------------------------------
\section{Responsibilities}
All SiLab team members are required to obey these rules.

%------------------------------------------------------------------
\section{Principles}

\subsection{Gantry}
The gantry code comprises of proprietary software and custom code in LabView, VisualBasic, and C++. All components are necessary to operate the gantry.
\begin{itemize}
    \item \textbf{Gantry software.} In case of disaster recovery, the following software needs to be reinstalled: Aerotec Motion Composer, MatLab and LabView 2011 (or newer).
    \item \textbf{LabView code.} The code is stored in a \texttt{git} repository, regularly replicated to \url{https://git.unl.edu/jmonroy2/glueing}. This includes the pattern recognition part, written in-house in C++. Recovery requires a clone of that repository plus configuration work.
    \item \textbf{Data.} Logfiles are kept locally, no backup foreseen so far.
\end{itemize}
TODO: This covers glueing only. Where is the potting code stored?

\subsection{Wirebonder}
The wirebonder is operated by a PC running Windows XP embedded into the machine. The software is unavailable on more recent versions of Windows. For security reasons, no network access is allowed. All backup and transfer of user data has to make use of a USB thumb drive.
\begin{itemize}
    \item \textbf{Bond programs.} These programs are custom to accommodate our modules. TODO: Establish rule how this is transferred and stored. Preferrably to git.unl.edu like all the other stuff.
    \item \textbf{Machine configuration.} This cannot be stored in a better way than as screenshots. TODO: Add this to the rep of bond programs or put it on th eUNL wirebonding TWiki.
    \item \textbf{Logfiles.} Logfiles are kept locally, no backup foreseen so far.
    \item \textbf{Data.} Mostly test results from pull tests. Need to be transferred using a USB thumbdrive.
\end{itemize}

\subsection{Test stands}
Test stands operate software developed by the CMS pixel community (\texttt{pXar}, \texttt{ElCommandante}, \texttt{psi46test}) using DTB and in one case control the cold box.
\begin{itemize}
    \item \textbf{Source code.} All source code is available for download on \texttt{https://github.com/psi46} and can be compiled according to instructions available at \url{https://twiki.cern.ch/twiki/bin/viewauth/CMS/Psi46}.
    \item \textbf{Configuration.} Any special configuration needs to be documented, preferrably inside the colection of UNL TWiki pages TODO: Discuss this
    \item \textbf{Logfiles.} Logfiles are kept locally, no backup foreseen so far.
    \item \textbf{Data.} TODO: How do we store this stuff? Using moreweb (like BPix and Purdue)? Database?
\end{itemize}

\subsection{UNLHEP electronic logbook}
The elog is an instance of the electronic logbook software available at \url{https://midas.psi.ch/elog/}. Our installation is hosted on the UNL Tier3 datacenter and its data is included in the regular backup.
% Gerhan Attbury at T2/T3

\subsection{Purdue database}
This is used to store aggregated results and to manage workflows. The database is hosted and maintained by our colleagues at Purdue. It is accessed through a web interface. Backup and recovery is a responsibility of Purdue.

\subsection{Fermilab database}
At the time of writing, this database is not yet productive. Hosting, maintenance, backup and recovery are responsibilities of our colleagues at Fermilab.

\end{document}

